Efficient and Effective Metric Space Indexing for Complete Record Linkage Al: Exploring approaches to probabilistic record linkage using similarity searching (metric space indexing?)

### 2017-11-06 paper.tex
Update on Overleaf.

% MAX 200 words
\begin{abstract}
Probabilistic record linkage is the process of identifying records that refer to
the same real-world entities across two or more databases in situations where entity identifiers are unavailable.
It requires  similarities between records to be approximated using common attributes (such as names, addresses, phone numbers) and for pairs of records to be classified as matches or non-matches.
Record linkage is usually done as a two step process;  in the
first step a blocking or indexing is employed to efficiently identify
candidate record pairs which are then compared in more detail and
classified in the second step.

@@

We propose an metric indexing approach to \emph{complete} record
linkage, which ensures all record pairs that have a similarity above
a certain similarity threshold are being \textbf{compared}, while no pairs
with a similarity below the threshold are \textbf{compared}. Our approach
leads to a one-step record linkage process which combines indexing
with comparison and classification resulting in improved
effectiveness and efficiency as we experimentally evaluate on several
real-world databases.

>>>>

% MAX 200 words
\begin{abstract}
Probabilistic record linkage is the process of identifying records that refer to
the same real-world entities across two or more databases in situations where entity identifiers are unavailable.
It requires  similarities between records to be approximated using common attributes (such as names, addresses, phone numbers) and for pairs of records to be classified as matches or non-matches.
Record linkage is usually performed in a two step process;  in the
first step a blocking or indexing is employed to efficiently group similar
candidate record pairs which are then compared in more detail and
classified in the second step.

@@

We propose an metric indexing approach to \emph{complete} record
linkage, which ensures all record pairs that have a similarity above
a certain similarity threshold are being \textbf{compared}, while no pairs
with a similarity below the threshold are \textbf{compared}. Our approach
leads to a one-step record linkage process which combines indexing
with comparison and classification resulting in improved
effectiveness and efficiency as we experimentally evaluate on several
real-world databases.
Parameter space: good linkage bad linkage don't know which without ground truth. M Trees always high no config -> high confidence.
